### 2012-05-17 trunk/GUIErrorDetector/paper/evaluation.tex
small tweak

Five subjects (EclipseRunner, HudsonEclipse, SGTPuzzler, Fennec, and MyTracks)
are selected because they have known invalid thread access errors (1 error per subject) and
all errors have been fixed in later revisions.
We used the buggy versions to check whether our tool
can correctly identify those known errors. 
For the other five subjects, we selected them
by first searching for the
framework keywords (e.g., ``Java Swing'' or ``Java SWT'')
in the above source repositories, and then choosing subjects based on the following
criteria. First, the subject must be a Java application, not
an open library. Second, the subject must use multithreading in its implementation.
Third, the subject is listed in the first 5 result pages.
This permits us to exclude immature subjects that may contain obvious errors.
For each selected subject, we ran our tool on the latest stable release to find new errors.
%of each project to check whether
%it can find any new errors.

@@

We manually determined the validity of each warning.
For a known error, we compared the generated report (i.e., an
error-revealing method call chain as shown in Figure~\ref{fig:report}) against the
actual bug-fixing patch to check whether the tool identified the
buggy method. For a previously-unknown error, we submitted a new bug
report to its developers, and wrote a test driver to reproduce it.
%wrote a test driver to

@@

As shown in Table~\ref{table:results}, our tool found
errors in each subject. Using the 1-CFA
call graph algorithm, our tool issued 22 warnings, among
which \bugs warnings reveal \bugs distinct errors (\newbugs were previously unknown,
and the \oldbugs known errors were correctly identified),
2 warnings are false positives, and the remaining 8 warnings
are redundant. Section~\ref{sec:reflectionaware} compares with other call graph
construction algorithms.

@@

\noindent This variant returns the shortest path from any \CodeIn{Thread.start()} node
to any UI-accessing node, rather than the shortest path from each
\CodeIn{Thread.start()} node to any UI-accessing node as the algorithm in
Figure~\ref{fig:detectalgorithm} does.
This variant reported 10 errors and 12 false positives.   It missed 1 error in S3dropbox and 1 error in
SudokuSolver.
It visits every node in the call graph only once, rather than potentially
once per entry node, but doing so prunes out real error paths.

The second variant uses one DFS per entry node, by changing
the $\mathit{worklist}$ on line 7 of Figure~\ref{fig:detectalgorithm} to
a stack, and changing queue operations dequeue and enqueueAll
on lines 10 and 21
to pop and pushAll.
This variant reported 11 errors and 10 false positives.  It missed 1 error in FileBunker.
DFS tends to search deeper into the graph and return longer paths that are
more likely to be infeasible or to be removed by the filters.
%For the FileBunker subject, paths
%returned by DFS are much longer than BFS, and do not actually exist.

>>>>

Five subjects (EclipseRunner, HudsonEclipse, SGTPuzzler, Fennec, and MyTracks)
are selected because they have known invalid thread access errors (1 error per subject) and
all errors have been fixed in later revisions.
We used the buggy versions to check whether our tool
can correctly identify those known errors. 
For the other four subjects, we selected them
by first searching for the
framework keywords (e.g., ``Java Swing'' or ``Java SWT'')
in the above source repositories, and then choosing subjects based on the following
criteria. First, the subject must be a Java application, not
an open library. Second, the subject must use multithreading in its implementation.
Third, the subject is listed in the first 5 result pages.
This permits us to exclude immature subjects that may contain obvious errors.
For each selected subject, we ran our tool on the latest stable release to find new errors.
%of each project to check whether
%it can find any new errors.

@@

We manually determined the validity of each warning.
For a known error, we compared the generated report (i.e., an
error-revealing method call chain as shown in Figure~\ref{fig:report}) against the
actual bug fix to check whether the tool identified the
buggy method. For a previously-unknown error, we submitted a new bug
report to its developers, and wrote a test driver to reproduce it.
%wrote a test driver to

@@

As shown in Table~\ref{table:results}, our tool found
errors in each subject. Using the 1-CFA
call graph algorithm, our tool issued \warnings warnings, among
which \bugs warnings reveal \bugs distinct errors (\newbugs were previously unknown,
and the \oldbugs known errors were correctly identified),
2 warnings are false positives, and the remaining 8 warnings
are redundant. Section~\ref{sec:reflectionaware} compares with other call graph
construction algorithms.

@@

\noindent This variant returns the shortest path from any \CodeIn{Thread.start()} node
to any UI-accessing node, rather than the shortest path from each
\CodeIn{Thread.start()} node to any UI-accessing node as the algorithm in
Figure~\ref{fig:detectalgorithm} does.
This variant reported 8 errors and 12 false positives.   It missed 1 error in S3dropbox and 1 error in
SudokuSolver.
It visits every node in the call graph only once, rather than potentially
once per entry node, but doing so prunes out real error paths.

The second variant uses one DFS per entry node, by changing
the $\mathit{worklist}$ on line 7 of Figure~\ref{fig:detectalgorithm} to
a stack, and changing queue operations dequeue and enqueueAll
on lines 10 and 21
to pop and pushAll.
This variant reported 9 errors and 10 false positives.  It missed 1 error in FileBunker.
DFS tends to search deeper into the graph and return longer paths that are
more likely to be infeasible or to be removed by the filters.
%For the FileBunker subject, paths
%returned by DFS are much longer than BFS, and do not actually exist.
